On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-07 AvdMomZvol_rails/Article.tex
[AMZr] An example of 3-8-rails set

>>>>

On Fig.~\ref{11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png} we show the following rails set with 3 points on one line and 8 points on the other:
\begin{multline*}
\mathcal{P}_{3,8}=\sqrt{255255}/2*\{
	( 1767 ; -3);
	( 2791 ; -3);
	( 4071 ; -3);
\\
	( -306 ; 0);
	( 0 ; 0);
	( 1798 ; 0);
	( 2304 ; 0);
	( 2760 ; 0);
	( 3534 ; 0);
	( 4040 ; 0);
	( 4558 ; 0)
\}
\end{multline*}
It's notable that $\operatorname{char} \mathcal{P}_{3,8}=255255 = 3 \cdot 5 \cdot 7 \cdot 11 \cdot 13 \cdot 17$
is a production of the first 6 odd primes,
and the distances between the three points on the bottom line are $512=2^{9}$, $640=2^7 \cdot 5$ and
$512+640 = 1152 = 2^7 \cdot 3^2$.

\begin{figure}[h!]
	\center{\includegraphics[width=0.9\linewidth]{11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}}
	\parbox{0.9\linewidth}{\caption{PIPS of cardinality 11 and diameter 2423}
	\label{11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}}
\end{figure}
